---
title: "RMarkdown template for assignment 1"
author: "Your Name"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
### NB (Nota bene): This initial code chunk contains any and all packages and package options that will be used in this project
knitr::opts_chunk$set(echo = FALSE, message=FALSE) # by default, when you knit this file (which will default knit to Word), you will not see the commands or warning messages echoed.

### Loading packages
  # When I use external packages that aren't "base R", I load them into the workspace here with the library(package name) command.
library(tidyverse) # load the Tidyverse set of packages that supplement base R functionalities like data.frame, reading in spreadsheet data (read_csv, etc.)
library(googlesheets4) # package that provides a convenient interface in R to interact with Google spreadsheets
library(knitr) # this is the package that knits Rmarkdown files to HTML, Word, or PDF; we'll be using the kable() function in this package to make nice tables for Word
library(vader) # this is the package we will be using for sentiment analysis
library(tidytext) # this is the package we will use for wrangling text data
library(stringr) # package with helpful functions dealing with string, or character/text data.
library(tokenizers) # package to split strings into smaller entities (e.g. messages into words, ngrams, or individual letters)
library(lattice) # package that extends base R plot visualizations
library(Hmisc) # package that has helpful visualization tools for our data

  # Package options
options(gargle_oauth_email="YOUREMAIL@gmail.com") # this lets RMarkdown knit successfully by using your stored token for your Google account. PLEASE MAKE SURE that you change this to your email account.
```

# Issue(s)

*NB: you can rename this section header to your issue(s)*

Issue XYZ is a prominent challenge...
I chose/I focused on issues ...

## Role of public mobilization for issue(s)

Issue XYZ relies on public funding/voting/... as such, voter mobilization/citizen science/public engagement is critical to ...

# Hypotheses

For issue(s) XYZ, I will be testing ...

# Data search and curation process

To advance environmental social media communications on ISSUE(S) X (replace with your issue), I focused on the following search terms:

* Search term 1
* Search term 2
* .. Search term j

Initially, I started with a longer set of search terms / fewer search terms (`term 1, term 2, term 3...term M`). However, I realized that these terms / the data that these terms yielded .../These terms produced posts that deviated from Issue XYZ in ... these ways. As such, I iteratively identified the search terms above as the final set of terms to source posts clearly focused on Issue XYZ.

I chose site(s) ABC because ... Instagram is a major site for a current public awareness campaign/Twitter discourse is driving opinion formation on Issue XYZ/Facebook is ... (Other sites are also OK, but must feature meaningful text data to meet this project's requirements.)

## Interacting with dataset

Below, I show the first six rows of my environmental social media dataset, focused on issue X (replace with your own issue). The subsequent section describes the columns in my data.

```{r read_envDF}
envDF <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1K-tgni6JJ33x1mG-rxNFopnC8sBuRzVLd5loBO0e1jk/edit?usp=sharing") # provide the sharing link to your own spreadsheet here to modify this code for your project.

head(envDF)
```

* Column 1: This column presents variable 1
* Column 2: Variable 2
* Column n: Variable n

